{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-01-24 documents/background.tex
Building the thing

>>>>

for which our working hypothesis is that there are no clinically useful mechanisms,

It stands to reason, then, that any pulse longer than the relaxation time is not efficiently.

Less than 1 nanosecond (where poration and thermal effects start to become significant, and any previous absorbed power has been dispersed in the solvent) but greater than about 10 picoseconds (covered by existing laser research) and electric fields between 0.1 MV/m (for which biological effects at these timescales are only barely plausible) and 10 MV/m (the production of pulses which strain credulity).

as dt decreases, there's lots of room to add more zeros. a pulse 4 orders of magnitude higher than the maximum field used by practically any existing system.

### 2021-01-24 documents/brillouin_pulse_math.tex
Building the thing

Uzunoglu \cite{Theoretical2020} mention a handy way to circumvent this lossy-flesh problem: the Brillouin and Sommerfeld precursors.

@@

The highly dispersive nature of tissue, which causes a peculiar distortion of short pulses,

The change in loss (the complex part of the permittivity, or the) and increase in penetration depth

A third aspect leads to the formation of the prototypical brilluoin precursor: any "sharp" 
beginning or end of a tone, or other spatially confined structure in a waveform, includes harmonics 
up to these \footnotemark

@@

@@

\begin{figure}[H]
	%	\makebox[\textwidth][c]{
	\includesvg[width=\textwidth]{muscle_pulse_8cm_minimize_test1}
	\caption{Second.}
\end{figure}

@@

 Believed to be FFT window artifacts. Increasing the window size with the same sample rate caused CG convergence to stall.

>>>>

Uzunoglu \cite{Theoretical2020} mention a handy way to circumvent this lossy-flesh problem: the Brillouin and Sommerfeld precursors, and dispersion in general.

@@

\begin{itemize}
	\item The highly dispersive nature of tissue, which causes a peculiar distortion of short pulses,
	\item The variation in loss (the imaginary part of the complex permittivity) and penetration depth versus frequency. 
\end{itemize}

A third aspect leads to the formation of the prototypical Brillouin precursor specifically: any sharp 
beginning or end of a tone, or other sharply defined structure in a waveform, includes harmonics beyond the tone's carrier wave up to the rise time \footnotemark. \wikinote{add image}

@@

By putting more power in higher frequencies,

@@

\begin{figure}[H]
	%	\makebox[\textwidth][c]{
	\includesvg[width=\textwidth]{muscle_pulse_8cm_minimize_test1}
	\caption{}
\end{figure}

The (noisy) output of the optimization for z=0.08 m in muscle. The low-frequency component is believed to be due to the FFT window size. Increasing the window size with the same sample rate caused CG convergence to stall. However, it's interesting that this appears to result in a larger amplitude.

@@
